StreamReduce: Processing Data Streams\\and Avoiding Work

### 2012-05-10 paper/paper.tex
Prettify cluster config image
Tweak methodology section

\section{Methodology}
\label{sec:methodology}
The cluster I used to test StreamReduce is a 5-node network consisting of~1 spout,~1 fetcher,~4 workers,~1
collector, and~1 master. Roles were partitioned among nodes as shown in
Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM~\cite{sipb:xvm} VMs provisioned with~128MB RAM each.
The master, spout, fetcher, and collector ran on a mid-2010 Macbook Air laptop with~4GB of RAM.

\begin{figure}
\begin{verbatim}
                  |--------|
                - | worker |
               /  |--------|
|-----------| /   |--------|
| master    | --- | worker |
| spout     |     |--------|
| fetcher   |     |--------|
| collector | --- | worker |
|-----------| \   |--------|
               \  |--------|
                - | worker |
                  |--------|
\end{verbatim}
\caption{Topology of the test StreamReduce cluster used in the word count case study. Each box represents a single machine.}
\label{fig:clusterDiagram}
\end{figure}

@@

To serve the data, I munged it into a YAML file containing a hash of
\begin{center}
$\texttt{article\_id}\rightarrow\texttt{fulltext}$.
\end{center}
To store fulltext, I base64 encoded it and
deflated it using zlib. This requires workers to inflate and decode the fulltext before they
can process it further. The server reads from this YAML file and returns the resulting hash as
JSON.

@@

>>>>

\section{Methodology}
\label{sec:methodology}
The cluster I used to test StreamReduce is a 5-node network consisting of~1 spout,~1 fetcher,~4 workers,~1
collector, and~1 master. Roles were partitioned among nodes as shown in
Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM~\cite{sipb:xvm} VMs provisioned with~128MB RAM each.
The master, spout, fetcher, and collector ran on a mid-2010 Macbook Air laptop with~4GB of RAM. I configured
the cluster to kill tasks on the master node, before they were shipped to workers.

\begin{figure}
  \includegraphics[width=\linewidth]{sr-topology.png}
  \caption{Topology of the test StreamReduce cluster used in the word count case study. Each square box represents a single machine. Each rounded box represents a StreamReduce role.}
\label{fig:clusterDiagram}
\end{figure}

@@

To serve the data, I transformed it into a YAML file containing a hash of
\begin{center}
$\texttt{article\_id}\rightarrow\texttt{fulltext}$.
\end{center}
To store fulltext, I base64 encoded it and
deflated it using zlib. This requires workers to inflate and decode the fulltext before they
can process it further. The server reads from this YAML file and returns the resulting hash as
JSON.

@@

I ran four trials of the word count job for every combination of work level and task kill
rate I tested.
